Polynomial phase estimation by least squares phase unwrapping

### 2013-07-08 paper.tex
minor?

\begin{table}[t]
\centering
\begin{tabular}{lrrrrr}
 & LSU & LSU ($K$-best) & CPF & HAF & ZW \\ \toprule
$N=19$ & 10 & 10 & 8 & 11 & 31 \\ 
$N=49$ & 7 & 7 & 5 & 9 & 29 \\ 
$N=99$ & & 6 & 3 & 5 & 27 \\ 
$N=199$ & & 3 & 1 & 3 & 23 \\ 
$N=299$ & & 2 & -1 &  & \\ 
$N\to\infty$ & $-\infty$ & & & 3.77 & \\ \bottomrule
\end{tabular}
\caption{Estimated SNR threshold in decibels with $m=3$}
\label{tablm3}
\end{table}

>>>>

\begin{table}[t]
\centering
\begin{tabular}{lrrrrr}
 & LSU & LSU ($K$-best) & CPF & HAF & ZW \\ \toprule
$N=19$ & 10 & 10 & 8 & 11 & 31 \\ 
$N=49$ & 7 & 7 & 5 & 9 & 29 \\ 
$N=99$ & & 6 & 3 & 5 & 27 \\ 
$N=199$ & & 3 & 1 & 5 & 23 \\ 
$N=299$ & & 2 & -2 & 5 & \\ 
$N\to\infty$ & $-\infty$ & & & 3.77 & \\ \bottomrule
\end{tabular}
\caption{Estimated SNR threshold in decibels with $m=3$}
\label{tablm3}
\end{table}
